### 2020-03-31 reviews/SIGBOVIK_2020_review_18.tex
reviews: Restore Internet searches to their former lack of glory

%%% Replace the following text with your review.
I think the review currently for the guide to plants should probably be attributed to the originator of the couplet (Edward Lear) rather than to "Prof. James McCann" -- I'm not sure there's much joke added (since it ended up on a paper referencing me) and I'm not really comfortable with something I didn't write being attributed to me.

>>>>

%%% Replace the following text with your review.
I think the review currently for the guide to plants should probably be attributed to the originator of the couplet (Edward Lear) rather than to "Prof. Jim McCann" -- I'm not sure there's much joke added (since it ended up on a paper referencing me) and I'm not really comfortable with something I didn't write being attributed to me.
